CMPEN/EE 454 Project 2 Report

### 2015-12-12 p2/report/project_report.tex
input listings for important files

\documentclass{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{draftwatermark}
\usepackage {sectsty}
\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{ {img/} }
\usepackage [dvipsnames]{xcolor}

\lstset{ %
	language=C,
	basicstyle=\ttfamily\footnotesize,
	keywordstyle=\ttfamily\color{blue}\footnotesize,
	commentstyle=\color{OliveGreen}\ttfamily\footnotesize,
	texcl,
	escapechar =`
	escapebegin=\lst@commentstyle,
	showspaces=false,
	showtabs=false,
	numbers=left,
	showstringspaces=false,
	frame=single,
	tabsize=3
}
\makeatother

@@

An object contained with a bounding box is characterized by its corner points; these corner points are obtained by running the Harris Corner Detection algorithm.  To find correspondence sets between corner points and bounding boxes, the Munkres assignment algorithm is used.  Finally, RANSAC is used to obtain an inlier-set of correspondences which are used in translation estimation.  A description of these algorithms is found in Section \ref{algo}.

@@

\newpage
\subsection{Patch Matching}
\subsubsection{Synopsis}
After the corner point coordinates of each image has been computed, the bounding boxes for each image and corresponding corner points are passed to a patch matching routine.  This patch matching routine computes correspondences between corner points and between bounding boxes (explained in more detail below).  The in the system pictured below, assuming the image in bounding boxes 1 and 3 are similar and the images in bounding boxes 2 and 4 are similar, the correspondence set output for this phase would be:
\[
\left \{
\begin{tabular}{c}
$(1 \iff 3,\quad \text{assignment cost})$ \\
$(2 \iff 4,\quad \text{assignment cost})$
\end{tabular}
\right \}
\]
\includegraphics[width=\textwidth]{after_corner}
\subsubsection{Implementation}
To find an optimal bounding box correspondence set between two images, we first must compute cost values for matching two boxes.  Here is the implemented cost function:
\\
\begin{minipage}{\textwidth}
\begin{lstlisting}

@@

\end{lstlisting}
\end{minipage}
\\~\\
For the bounding boxes pictured below, here is an example assignment set:
\[
\left \{
\begin{tabular}{c}
$(G \iff J,\quad \text{SSD}_{GJ})$ \\
$(F \iff K,\quad \text{SSD}_{FK})$ \\
$(I \iff M,\quad \text{SSD}_{IM})$ \\
$(E \iff \emptyset,\quad \infty)$ \\
$(H \iff \emptyset,\quad \infty)$
\end{tabular}
\right \}
\]
The overall cost of assigning Bounding Box 1 to Bounding Box 2 is then the sum of the finite costs in the optimal assignment set; i.e. $\text{SSD}_{GJ} + \text{SSD}_{FK} + \text{SSD}_{IM}$.
\begin{center}
\fbox{\includegraphics[width=0.65\textwidth]{box_corners}}
\end{center}
~\\
A similar method is used to find an optimal bounding box correspondence between two images:
\\
\begin{minipage}{\textwidth}
\begin{lstlisting}

@@

>>>>

\documentclass{article}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{draftwatermark}
\usepackage {sectsty}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{underscore}
\usepackage{graphicx}
\usepackage[toc]{appendix}
\graphicspath{ {img/} }
\usepackage [dvipsnames]{xcolor}

\lstset{ %
	language=C,
	basicstyle=\ttfamily\footnotesize,
	keywordstyle=\ttfamily\color{blue}\footnotesize,
	stringstyle=\ttfamily\color{purple},
	commentstyle=\color{OliveGreen}\ttfamily\footnotesize,
	texcl,
	escapechar =`
	escapebegin=\lst@commentstyle,
	showspaces=false,
	showtabs=false,
	numbers=left,
	showstringspaces=false,
	frame=single,
	tabsize=3,
	breaklines=true,
	breakautoindent=true,
}
\makeatother

@@

An object contained with a bounding box is characterized by its corner points; these corner points are obtained by running the Harris Corner Detection algorithm.  To find correspondence sets between corner points and bounding boxes, the Munkres assignment algorithm is used.  Finally, RANSAC is used to obtain an inlier-set of correspondences which are used in translation estimation.  A description of these algorithms and pseudocode implementation is found in Section \ref{algo}.  The actual Matlab implementation of these functions is found in Appendix \ref{source}.

@@

\newpage
\subsection{Patch Matching}
\subsubsection{Synopsis}
After the corner point coordinates of each image has been computed, the bounding boxes for each image and corresponding corner points are passed to a patch matching routine.  This patch matching routine computes correspondences between corner points and between bounding boxes (explained in more detail below).  The in the system pictured below, assuming the image in bounding boxes 1 and 3 are similar and the images in bounding boxes 2 and 4 are similar, the correspondence set output for this phase would be:
\[
\left \{
\begin{tabular}{c}
$(1 \iff 3,\quad \text{assignment cost})$ \\
$(2 \iff 4,\quad \text{assignment cost})$
\end{tabular}
\right \}
\]
\includegraphics[width=\textwidth]{aftercorner}
\subsubsection{Implementation}
To find an optimal bounding box correspondence set between two images, we first must compute cost values for matching two boxes.  Here is the implemented cost function:
\\
\begin{minipage}{\textwidth}
\begin{lstlisting}

@@

\end{lstlisting}
\end{minipage}
\\~\\
For the bounding boxes pictured below, here is an example assignment set:
\[
\left \{
\begin{tabular}{c}
$(G \iff J,\quad \text{SSD}_{GJ})$ \\
$(F \iff K,\quad \text{SSD}_{FK})$ \\
$(I \iff M,\quad \text{SSD}_{IM})$ \\
$(E \iff \emptyset,\quad \infty)$ \\
$(H \iff \emptyset,\quad \infty)$
\end{tabular}
\right \}
\]
The overall cost of assigning Bounding Box 1 to Bounding Box 2 is then the sum of the finite costs in the optimal assignment set; i.e. $\text{SSD}_{GJ} + \text{SSD}_{FK} + \text{SSD}_{IM}$.
\begin{center}
\fbox{\includegraphics[width=0.65\textwidth]{boxcorners}}
\end{center}
~\\
A similar method is used to find an optimal bounding box correspondence between two images:
\\
\begin{minipage}{\textwidth}
\begin{lstlisting}

@@

\begin{appendices}
\section{Source Code Listings}\label{source}
% \lstinputlisting[escapechar=,language=Matlab,caption=blob2px.m,breaklines=true]{../matlab/blob2px.m}
\lstinputlisting[escapechar=,language=Matlab,caption=harris.m]{../matlab/harris.m}
\lstinputlisting[escapechar=,language=Matlab,caption=main.m, lastline=29]{../matlab/main.m}
\lstinputlisting[escapechar=,language=Matlab,caption=matcher.m, lastline=77]{../matlab/matcher.m}
\lstinputlisting[escapechar=,language=Matlab,caption=phase1.m]{../matlab/phase1.m}
\lstinputlisting[escapechar=,language=Matlab,caption=pruneMatrixScaled.m]{../matlab/pruneMatrixScaled.m}
\lstinputlisting[escapechar=,language=Matlab,caption=ransac.m]{../matlab/ransac.m}
\lstinputlisting[escapechar=,language=Matlab,caption=SumOfSqaureDifferences.m]{../matlab/SumOfSqaureDifferences.m}
\end{appendices}
